---
title: "Data 410 Project Rough Draft"
author: "Daniel Krasnov, Keiran Malott, Ross Cooper"
date: "2023-04-07"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

\newpage

# Guidelines
- An introduction to the dataset, and the scientific hypotheses you will investigate.

- A descriptive analysis of the data; give a detailed description about the data including
the number of variables, variables types, summary statistics, graphs of data, etc..

– A regression analysis that addresses your scientific hypothesis, using all the regression
model building techniques you have learned. Model and data appropriateness
diagnostics are expected. Plots and tables are highly encouraged, where you need to
include the interpretation for each plot/table.

– Conclusions and recommendations: give your conclusion based on your regression
analysis such as important variables identified, the most proper regression model you
have discovered, how your regression assumptions may be violated and how they affect
your results, etc

# Data Collection Method
describe how we scappred Not How Girls Work Subreddit

```{r Loading in data}
data <- read.csv("../data/NHGW.csv")
data <- data[,2:3]
head(data)
```

## Variable Description

Show example of our full data set show

## Data Preprocessing

Explain we only used Sarcastic and body columns. We used regex to remove /s. We then remove stopwords, lemmatize, etc.

# Feature Extraction Methods
interpreting text as data is lots of work say something about why that's tough and we need ways to vectorize text.

## TF-IDF

Explain tf-idf. Show what final result is for design matrix and explain how you got there.

## Word2Vec

Explain word2vec. Show what final result is for design matrix and explain how you got there.

## Glove

Explain Glove. Show what final result is for design matrix and explain how you got there.

# Regression Analysis
This analysis is a comparison of logistic model performance when using 3 types of feature extraction.

## Daniel's Analysis (better title later)



## Keiran's Analysis (better title later)

## Ross' Analysis (better title later)

