---
title: "Data 410 Project Rough Draft"
author: "Daniel Krasnov, Keiran Malott, Ross Cooper"
date: "2023-04-07"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Libraries, include=FALSE}
# Loading libraries
library(tm)
library(MLmetrics)
library(glmnet)
library(qdapRegex)
library(car)
library(plm)
library(reshape2)
library(tidyverse)
library(glmnet)
library(ggplot2)
```
\newpage

# Guidelines

- An introduction to the dataset, and the scientific hypotheses you will investigate.

- A descriptive analysis of the data; give a detailed description about the data including
the number of variables, variables types, summary statistics, graphs of data, etc..

– A regression analysis that addresses your scientific hypothesis, using all the regression
model building techniques you have learned. Model and data appropriateness
diagnostics are expected. Plots and tables are highly encouraged, where you need to
include the interpretation for each plot/table.

– Conclusions and recommendations: give your conclusion based on your regression
analysis such as important variables identified, the most proper regression model you
have discovered, how your regression assumptions may be violated and how they affect
your results, etc

# Data Collection Method
describe how we scappred Not How Girls Work Subreddit

```{r Loading in data}
# Load in data
data <- read.csv("../data/NHGW.csv")
data <- data[,2:3]
```

## Variable Description

Show example of our full data set show

## Data Preprocessing

Explain we only used Sarcastic and body columns. We used regex to remove /s. We then remove stopwords, lemmatize, etc.

# Feature Extraction Methods
interpreting text as data is lots of work say something about why that's tough and we need ways to vectorize text.

## TF-IDF

Explain tf-idf. Show what final result is for design matrix and explain how you got there.

```{r Create Corpus}
y <- data$Sarcastic
doc_id <- 1:nrow(data)
data$doc_id <- doc_id
data_clean <- data[,c("Body","doc_id")]
colnames(data_clean)[1] <- "text"
data_clean$text <- rm_non_words(data_clean$text)

# Construct Corpus
ds <- DataframeSource(data_clean)
corpus <- Corpus(ds)
```

```{r Clean Corpus}
# Clean the Corpus
# Remove punctuation
corpus <- tm_map(corpus, content_transformer(removePunctuation))
# Send everything to lower case
corpus <- tm_map(corpus, content_transformer(tolower))
# Remove stopwords
corpus <- tm_map(corpus, content_transformer(removeWords), 
          stopwords("english"))
# Remove whitespace
corpus <- tm_map(corpus, stripWhitespace)
# Remove numbers
corpus <- tm_map(corpus, content_transformer(removeNumbers))
# Stemming
corpus <- tm_map(corpus, stemDocument)
```

```{r Create TF-IDF DTM}
# Create DTM object
dtm <- DocumentTermMatrix(corpus)
# Weight TF-IDF
tfidf_dtm <- weightTfIdf(dtm)
```



## Word2Vec

Explain word2vec. Show what final result is for design matrix and explain how you got there.

## Glove

Explain Glove. Show what final result is for design matrix and explain how you got there.

# Evaluation Metrics

Describe Precision, Recall, F1.

# Regression Analysis
This analysis is a comparison of logistic model performance when using 3 types of feature extraction.

## Daniel's Analysis (better title later)

### Base Model
The dimension of the DTM is too large by default. Can't use bestGLM as too many predictors. Do form of best subset by checking quantities of TF-IDF.

```{r Creating Quantile List}
# Set seed
set.seed(874)

# Do 80/20 train/test split
train_idx <- sample(1:nrow(data),floor(.8*(nrow(data))))
test_idx <- setdiff(1:nrow(data),train_idx)

# Get quantiles
tfidf_mat <- as.matrix(tfidf_dtm[train_idx,])

tfidf_vec <- as.vector(tfidf_mat)

tfidf_vec <- tfidf_vec[tfidf_vec > 0]

quants <- quantile(tfidf_vec, probs = seq(0.1,0.95,0.05))

# Only keep quantiles that result in matrices with fewer columns than rows
cols <- c()
for (quant in quants) {
  cols <- c(cols, ncol(tfidf_dtm[train_idx,tfidf_dtm$v > quant]))
}

 numRows <- nrow(tfidf_dtm[train_idx,])
 quants <- quants[which(cols < numRows)]
```

```{r Perform Best Subset Regression, cache=TRUE, message=FALSE,warning=FALSE}
# Get AICs for different subsets
models_aic <- list()
for (quant in quants) {
  # Filter DTM
  tfidf_dtm_r <- tfidf_dtm[train_idx, tfidf_dtm$v > quant]
  
  # Construct dataframe for fitting
  x <- as.data.frame(as.matrix(tfidf_dtm_r))
  y_train <- y[train_idx]
  data <- cbind(y_train, x)
  
  # Fit model
  glm.out <- glm(y_train ~ ., family = binomial, data)
  models_aic <- append(models_aic, glm.out$aic)
}

# Get best quantitle threshold by AIC
thresh <- quants[which.min(models_aic)]
```
The 95% percentile gave the best AIC so this is the base model I will select.

```{r Fit 95th Percentile Mode, warning=FALSE}
# Filter DTM
tfidf_dtm_r <- tfidf_dtm[train_idx,tfidf_dtm$v > thresh  ]

# Construct dataframe for fitting
x <- as.data.frame(as.matrix(tfidf_dtm_r))
y_train <- y[train_idx]
data <- cbind(y_train,x)

# Fit model
glm.out <- glm(y_train~., family = binomial, data)

# Percent reduction in deviance
per_dev_red_base <- 1 - glm.out$deviance/glm.out$null.deviance
```

There are several NAs, not good. Let's get results.

```{r Train Metrics for Base}
# Get predictions
predict.out <- predict(glm.out, type = "response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[train_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_base_train <- Recall(y_true, y_pred, positive = 1)
Pr_base_train <- Precision(y_true, y_pred, positive = 1)
F1_base_train <- F1_Score(y_true, y_pred, positive = 1)
```

```{r Test Metrics for Base, warning=FALSE}
# Get predictions
test_data <- cbind(as.data.frame(as.matrix(tfidf_dtm[test_idx,])))
predict.out <- predict(glm.out, newdata = test_data ,type="response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess,y[test_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_base_test <- Recall(y_true, y_pred, positive = 1)
Pr_base_test <- Precision(y_true, y_pred, positive = 1)
F1_base_test <- F1_Score(y_true, y_pred, positive = 1)
```

```{r VIFs Base Model, warning=FALSE}
# Cannot use VIF if there are NAs, remove them
dropterms <-
  names(glm.out$coefficients[is.na(glm.out$coefficients)])
x <- x[, which(!(colnames(x) %in% dropterms))]
data <- cbind(y_train, x)
glm.out <- glm(y_train ~ ., family = binomial, data)

# 6 VIFs over 10 serious collinearity problems
VIFs_base <- vif(glm.out) 
```
High VIFs, bad need to reduce collineairty. We try PCA now.

### PCA

We keep up to 90th percentile

```{r Perform PCA, warning=FALSE}
pca.out <- prcomp(as.data.frame(as.matrix(tfidf_dtm_r)))
pca.out.test <- predict(pca.out, as.data.frame(as.matrix(tfidf_dtm[test_idx,])))

# 90th cumulative proportion is given by PC1:PC16
pcs <- as.data.frame(pca.out$x[,1:16])
train_data <- cbind(y_train,pcs)
test_data <- as.data.frame(pca.out.test[,1:16])

# Fit model
glm.out <- glm(y_train~., family = binomial, train_data)

# Percent reduction in deviance
per_dev_red_PCA <- glm.out$deviance/glm.out$null.deviance # note this is actually an increase by a factor of 25.17876
```

```{r Train Metrics for PCA}
# Get predictions
predict.out <- predict(glm.out, type = "response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[train_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_PCA_train <- Recall(y_true, y_pred, positive = 1)
Pr_PCA_train <- Precision(y_true, y_pred, positive = 1)
F1_PCA_train <- F1_Score(y_true, y_pred, positive = 1)
```

```{r Test Metrics for PCA, warning=FALSE}
# Get predictions
predict.out <- predict(glm.out, newdata = test_data ,type="response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess,y[test_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_PCA_test <- Recall(y_true, y_pred, positive = 1)
Pr_PCA_test <- Precision(y_true, y_pred, positive = 1)
F1_PCA_test <- F1_Score(y_true, y_pred, positive = 1)
```

Very not good predicts everything as not sar.

```{r VIFs PCA Model, warning=FALSE}
# All 1
VIFs_PCA <- vif(glm.out) 
```

### LASSO
```{r Fit LASSO}
# Construct dataframe for fitting
x <- as.data.frame(as.matrix(tfidf_dtm[train_idx,]))
y_train <- y[train_idx]
data <- cbind(y_train,x)
test_data <- cbind(as.data.frame(as.matrix(tfidf_dtm[test_idx,])))

# Perform CV
glmnet.cv.out <- cv.glmnet(as.matrix(x),y_train,family="binomial",alpha = 1)
best_lambda <- glmnet.cv.out$lambda.min

# Fit best found model
glmnet.out <- glmnet(as.matrix(x),y_train,family="binomial",alpha = 1,lambda = best_lambda)
```

```{r Train Metrics for LASSO, warning=FALSE}
# Get predictions
predict.out <- predict(glmnet.out, as.matrix(x),type = "response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[train_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$s0

# Get metrics
Re_LASSO_train <- Recall(y_true, y_pred, positive = 1)
Pr_LASSO_train <- Precision(y_true, y_pred, positive = 1)
F1_LASSO_train <- F1_Score(y_true, y_pred, positive = 1)
```

```{r Test Metrics for LASSO, warning=FALSE}
# Get predictions
test_data <- as.matrix(tfidf_dtm[test_idx,rownames(glmnet.out$beta)])
predict.out <- predict(glmnet.out,newx = test_data,type="response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[test_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$s0

# Get metrics
Re_LASSO_test <- Recall(y_true, y_pred, positive = 1)
Pr_LASSO_test <- Precision(y_true, y_pred, positive = 1)
F1_LASSO_test <- F1_Score(y_true, y_pred, positive = 1)
```

### Weighted Base Model

```{r Get results for weighted base model, warning=FALSE}
# Recreate DTM
tfidf_dtm_r <- tfidf_dtm[train_idx, tfidf_dtm$v > thresh]

# Construct dataframe for fitting
x <- as.data.frame(as.matrix(tfidf_dtm_r))
y_train <- y[train_idx]
data <- cbind(y_train, x)
test_data <- cbind(as.data.frame(as.matrix(tfidf_dtm[test_idx, ])))
results_base_weighted <-
  data.frame(Re = NA,
             Pr = NA,
             F1 = NA,
             w1 = NA)

# For each weight calculate metrics
for (w1 in seq(0, 1, 0.01)) {
  weights <- c()
  # w1 = 0.01
  w2 = 1 - w1
  
  for (i in 1:length(y_train)) {
    if (y_train[i] == 1) {
      weights <- c(weights, w1)
    } else{
      weights <- c(weights, w2)
    }
  }
  
  # Fit model
  glm.out <-
    glm(y_train ~ .,
        family = binomial,
        data = data,
        weights = weights)
  
  # Get results
  predict.out <-
    predict(glm.out, newdata = test_data , type = "response")
  predict.out[which(predict.out >= 0.5)] <- 1
  predict.out[which(predict.out < 0.5)] <- 0
  guess <- data.frame(predict.out)
  output <- cbind(guess, y[test_idx])
  colnames(output)[2] <- "truth"
  y_true <- output$truth
  y_pred <- output$predict.out
  
  # Get metrics
  Re <- Recall(y_true, y_pred, positive = 1)
  Pr <- Precision(y_true, y_pred, positive = 1)
  F1 <- F1_Score(y_true, y_pred, positive = 1)
  
  results_base_weighted <-
    rbind(results_base_weighted, data.frame(
      Re = Re,
      Pr = Pr,
      F1 = F1,
      w1 = w1
    ))
}
results_base_weighted <- na.omit(results_base_weighted)
```

```{r Visualize results_base_weighted}
# Reshape data 
results_long <- melt(results_base_weighted, id.vars = "w1", 
                     variable.name = "y_var", value.name = "value")

# Visualize
ggplot(results_long, aes(x = w1, y = value, color = y_var)) +
  geom_point()
```
We want a F1 that balances Recall and Precision but still focuses on Recall. Anything around 0.75 is good.

```{r Fit optimal base weighting, warning=FALSE}
# Fit model
w1 = 0.75
w2 = 1 - w1
weights <- c()

for (i in 1:length(y_train)) {
  if (y_train[i] == 1) {
    weights <- c(weights, w1)
  } else{
    weights <- c(weights, w2)
  }
}

# Fit model
glm.out <-
  glm(y_train ~ .,
      family = binomial,
      data = data,
      weights = weights)

# Percent reduction in deviance
per_dev_red_base_weighted <- 1 - glm.out$deviance/glm.out$null.deviance
```


```{r Test Metrics for Base Weighted, warning=FALSE}
# Get predictions
test_data <- cbind(as.data.frame(as.matrix(tfidf_dtm[test_idx, ])))
predict.out <-
  predict(glm.out, newdata = test_data , type = "response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[test_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_base_weighted_test <- Recall(y_true, y_pred, positive = 1)
Pr_base_weighted_test <- Precision(y_true, y_pred, positive = 1)
F1_base_weighted_test <- F1_Score(y_true, y_pred, positive = 1)
```

```{r VIFs Base Weighted Model, warning=FALSE}
# Cannot use VIF if there are NAs, remove them
dropterms <-
  names(glm.out$coefficients[is.na(glm.out$coefficients)])
x <- x[, which(!(colnames(x) %in% dropterms))]
data <- cbind(y_train, x)
glm.out <- glm(y_train ~ ., family = binomial, data)

# 5 VIFs over 10
VIFs_weighted_base <- vif(glm.out) 
```

### Weighted PCA

```{r Get results for weighted PCA model, warning=FALSE}
# Recreate DTM
tfidf_dtm_r <- tfidf_dtm[train_idx, tfidf_dtm$v > thresh]

pca.out <- prcomp(as.data.frame(as.matrix(tfidf_dtm_r)))
pca.out.test <- predict(pca.out, as.data.frame(as.matrix(tfidf_dtm[test_idx,])))

# 90th cumulative proportion is given by PC1:PC24
pcs <- as.data.frame(pca.out$x[,1:24])
train_data <- cbind(y_train,pcs)
test_data <- as.data.frame(pca.out.test[,1:24])

# Create results dataframe
results_weighted_pca <-
  data.frame(Re = NA,
             Pr = NA,
             F1 = NA,
             w1 = NA)

# For each weight calculate metrics
for (w1 in seq(0, 1, 0.01)) {
  weights <- c()
  # w1 = 0.01
  w2 = 1 - w1
  
  for (i in 1:length(y_train)) {
    if (y_train[i] == 1) {
      weights <- c(weights, w1)
    } else{
      weights <- c(weights, w2)
    }
  }
  
  # Fit model
  glm.out <-
    glm(y_train ~ .,
        family = binomial,
        data = train_data,
        weights = weights)
  
  # Get results
  predict.out <-
    predict(glm.out, newdata = test_data , type = "response")
  predict.out[which(predict.out >= 0.5)] <- 1
  predict.out[which(predict.out < 0.5)] <- 0
  guess <- data.frame(predict.out)
  output <- cbind(guess, y[test_idx])
  colnames(output)[2] <- "truth"
  y_true <- output$truth
  y_pred <- output$predict.out
  
  # Get metrics
  Re <- Recall(y_true, y_pred, positive = 1)
  Pr <- Precision(y_true, y_pred, positive = 1)
  F1 <- F1_Score(y_true, y_pred, positive = 1)
  
  results_weighted_pca <-
    rbind(results_weighted_pca, data.frame(
      Re = Re,
      Pr = Pr,
      F1 = F1,
      w1 = w1
    ))
}
results_weighted_pca <- na.omit(results_weighted_pca)
```

```{r Visualize results_base_weighted}
# Reshape data 
results_long <- melt(results_weighted_pca, id.vars = "w1", 
                     variable.name = "y_var", value.name = "value")

# Visualize
ggplot(results_long, aes(x = w1, y = value, color = y_var)) +
  geom_point() 
```
F1 holds pretty steady. We go for the one that has the highest Recall, a reasonable precision, and w good F1. 0.62 has 

```{r Fit optimal PCA weighting, warning=FALSE}
# Fit model
w1 = 0.62
w2 = 1 - w1
weights <- c()

for (i in 1:length(y_train)) {
  if (y_train[i] == 1) {
    weights <- c(weights, w1)
  } else{
    weights <- c(weights, w2)
  }
}

# Fit model
glm.out <-
  glm(y_train ~ .,
      family = binomial,
      data = train_data,
      weights = weights)

# Percent reduction in deviance
per_dev_red_PCA <- glm.out$deviance/glm.out$null.deviance # note this is actually an increase by a factor of 19.96864
```

```{r Train Metrics for Weighted PCA}
# Get predictions
predict.out <- predict(glm.out, type = "response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[train_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_weighted_PCA_train <- Recall(y_true, y_pred, positive = 1)
Pr_weighted_PCA_train <- Precision(y_true, y_pred, positive = 1)
F1_weighted_PCA_train <- F1_Score(y_true, y_pred, positive = 1)
```

```{r Test Metrics for Weighted PCA, warning=FALSE}
# Get predictions
predict.out <- predict(glm.out, newdata = test_data ,type="response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess,y[test_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_weighted_PCA_test <- Recall(y_true, y_pred, positive = 1)
Pr_weighted_PCA_test <- Precision(y_true, y_pred, positive = 1)
F1_weighted_PCA_test <- F1_Score(y_true, y_pred, positive = 1)
```

```{r VIFs Weighted PCA Model, warning=FALSE}
# All 1
VIFs_weighted_PCA <- vif(glm.out) # none over 10
```

### Weighted LASSO

```{r refit best LASSO}
# Construct dataframe for fitting
x <- as.data.frame(as.matrix(tfidf_dtm[train_idx,]))
y_train <- y[train_idx]
data <- cbind(y_train,x)
test_data <- cbind(as.data.frame(as.matrix(tfidf_dtm[test_idx,])))

# Fit best found model
glmnet.out <- glmnet(as.matrix(x),y_train,family="binomial",alpha = 1,lambda = best_lambda)
```

```{r Get results for weighted LASSO model, warning=FALSE}
# Construct dataframe for fitting
x <- as.data.frame(as.matrix(tfidf_dtm[train_idx, ]))
y_train <- y[train_idx]
data <- cbind(y_train, x)
test_data <- as.matrix(tfidf_dtm[test_idx, ])

# Create results dataframe
results_weighted_lasso <-
  data.frame(Re = NA,
             Pr = NA,
             F1 = NA,
             w1 = NA)

# For each weight calculate metrics
for (w1 in seq(0.01, 0.99, 0.01)) {
  weights <- c()
  # w1 = 0.1
  w2 = 1 - w1
  
  for (i in 1:length(y_train)) {
    if (y_train[i] == 1) {
      weights <- c(weights, w1)
    } else{
      weights <- c(weights, w2)
    }
  }
  
  # Fit model
  glmnet.out <-
    glmnet(
      as.matrix(x),
      y_train,
      family = "binomial",
      alpha = 1,
      lambda = best_lambda,
      weights = weights
    )
  
  # Get results
  predict.out <-
    predict(glmnet.out, newx = test_data , type = "response")
  predict.out[which(predict.out >= 0.5)] <- 1
  predict.out[which(predict.out < 0.5)] <- 0
  guess <- data.frame(predict.out)
  output <- cbind(guess, y[test_idx])
  colnames(output)[2] <- "truth"
  y_true <- output$truth
  y_pred <- output$s0
  
  # Get metrics
  Re <- Recall(y_true, y_pred, positive = 1)
  Pr <- Precision(y_true, y_pred, positive = 1)
  F1 <- F1_Score(y_true, y_pred, positive = 1)
  
  results_weighted_lasso <-
    rbind(results_weighted_lasso, data.frame(
      Re = Re,
      Pr = Pr,
      F1 = F1,
      w1 = w1
    ))
}
results_weighted_lasso <- na.omit(results_weighted_lasso)
```

```{r Visualize results_weighted_lasso}
# Reshape data 
results_long <- melt(results_weighted_lasso, id.vars = "w1", 
                     variable.name = "y_var", value.name = "value")

# Visualize
ggplot(results_long, aes(x = w1, y = value, color = y_var)) +
  geom_point() 
```
0.55 is best

```{r Fit optimal PCA weighting, warning=FALSE}
# Fit model
w1 = 0.55
w2 = 1 - w1
weights <- c()

for (i in 1:length(y_train)) {
  if (y_train[i] == 1) {
    weights <- c(weights, w1)
  } else{
    weights <- c(weights, w2)
  }
}

 # Fit model
  glmnet.out <-
    glmnet(
      as.matrix(x),
      y_train,
      family = "binomial",
      alpha = 1,
      lambda = best_lambda,
      weights = weights
    )
  
# Percent reduction in deviance
per_dev_red_weighted_Lasso <- glmnet.out$dev.ratio
```

```{r Train Metrics for Weighted PCA}
# Get predictions
predict.out <- predict(glm.out, type = "response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess, y[train_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_weighted_PCA_train <- Recall(y_true, y_pred, positive = 1)
Pr_weighted_PCA_train <- Precision(y_true, y_pred, positive = 1)
F1_weighted_PCA_train <- F1_Score(y_true, y_pred, positive = 1)
```

```{r Test Metrics for Weighted PCA, warning=FALSE}
# Get predictions
predict.out <- predict(glm.out, newdata = test_data ,type="response")
predict.out[which(predict.out >= 0.5)] <- 1
predict.out[which(predict.out < 0.5)] <- 0
guess <- data.frame(predict.out)

# Format output
output <- cbind(guess,y[test_idx])
colnames(output)[2] <- "truth"
y_true <- output$truth
y_pred <- output$predict.out

# Get metrics
Re_weighted_PCA_test <- Recall(y_true, y_pred, positive = 1)
Pr_weighted_PCA_test <- Precision(y_true, y_pred, positive = 1)
F1_weighted_PCA_test <- F1_Score(y_true, y_pred, positive = 1)
```


## Keiran's Analysis (better title later)

## Ross' Analysis (better title later)

